\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-10-02 appendices.tex
Corrected proof of isoprimetric lemma

Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
from \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case of $R_\Sigma = n$ and $L=n$, we get
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2017}, and leads to
\[
D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
\]
which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.

\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
\label{proof:thm:adpative_lower_bound}
}
Consider the following two Lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
\begin{equation}
\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
\leq  4f^2(0). 
\label{eq:lem_bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
\[
M(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $M$ with respect to $\theta$ is bounded from above by $\eta(0)$.
\end{lem}

@@

We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}. In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
\begin{equation}
\label{eq:general_messages}
B_i = \begin{cases}
X_i \in A_i & 1, \\
X_i \notin A_i & -1,
\end{cases} 
\end{equation}
where $A_i \subset \R$ is a Borel measurable set. 
%Indeed, any measurable function $M(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
\begin{align}
P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
\end{align}
where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
\begin{align}
I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$. From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$. The Van Trees inequality \cite{van2004detection, gill1995applications} now implies 
\begin{align*}
\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B^n)} + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
& \geq \frac{1}{ 4f^2(0) n + I_0}.
\end{align*}
\QEDA

@@

\begin{lem} \label{lem:bound_intervals_delta}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
\begin{equation}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left( \sum_{i=1}^n (-1)^{i+1} F(x_i) \right) \left(1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right) } 
\leq  \max_{i} \eta_\delta(x_i),
\label{eq:lem_bound_intervals_delta}
\end{equation}
where 
\[
\eta_\delta(x) \triangleq \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}. 
\]
\end{lem}

@@

\delta_n \triangleq \delta_n(x_1,\ldots,x_n) \triangleq \sum_{k=1}^{n} (-1)^{k+1} f(x_k),

@@

\Delta_n \triangleq \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{k=1}^n (-1)^{k+1} F(x_k). 

@@

Note that 

@@

\eta_\delta(x) =  \frac{  \left(\delta_1(x) \right)^{2+\delta}}{ (\Delta_1(x))^{1+\delta}
(1-\Delta_1(x))^{1+\delta}}. 

@@

Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable, with a non-increasing derivative $c'(x)$. We first prove the lemma under the assumption that 

@@

c'(x) \triangleq \frac{f'(x)}{f(x)}, 

@@

is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
We use induction on $n \in \N$ to show that the LHS of \eqref{eq:lem_bound_intervals_delta} is bounded from above by $\max_i \eta_\delta(x_i)$. The case $n=1$ is trivial. Assume that 
\frac{ \left( \delta_n \right)^{2+\delta}} 
{\left(\Delta_n\left(1- \Delta_n \right) \right)^{1+\delta} } \leq \max_i \eta_{\delta}(x_i)
\label{eq:lem_bound_intervals_proof}
for all integers up to $n = N-1$ and consider the case $n = N$. 

@@

The maximal value of the LHS of \eqref{eq:lem_bound_intervals_proof} is attained for the same $(x_1,\ldots,x_N) \in \R^N$ that attains the maximal value of 

@@

& g(x_1,\ldots, x_N) \triangleq  (2+\delta) \log \delta_N - (1+\delta) \log \Delta_N - (1+\delta) \log \left(1 - \Delta_N  \right),

@@

The partial derivative of $g(x_1,\ldots,x_N)$ with respect to $x_k$ is given by

@@

\frac{\partial  g}{\partial x_k} = \frac{(2+\delta) (-1)^{k+1} f'(x_k)}{\delta_N} -\frac{(1+\delta) (-1)^{k+1} f(x_k)}{\Delta_N } + \frac{(1+\delta)(-1)^{k+1} f(x_k)}{1-\Delta_N },

@@

and we conclude that the gradient of $g$ vanishes if and only if

@@

c'(x_k) = \frac{f'(x_k)}{f(x_k)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N} \right),\quad k=1,\ldots,N.

@@

Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $x_1 = \ldots = x_N$. For odd $N$ and $x_1=\ldots =x_N$, the LHS of \eqref{eq:lem_bound_intervals_proof} equals $\eta(x_1) = \max_i \eta(x_i)$ hence the statement holds. For even $N$ and any constant $d$, the limit of the LHS of \eqref{eq:lem_bound_intervals_proof} as $(x_1,\ldots,x_N)\rightarrow (d,\ldots,d)$ exists and equals zero. Therefore, the maximum of the LHS of \eqref{eq:lem_bound_intervals_proof} is not attained at the line $x_1=\ldots=x_N)$. We now consider the possibility that the LHS of \eqref{eq:lem_bound_intervals_proof} is maximized at the borders. That is, as one or more of the coordinates of $(x_1,\ldots,x_N)$ approaches $\pm \infty$,  or $\pm \epsilon$. As we assumed $x_1 \geq \ldots \geq x_N$, if $x_i = x_{i+1}$ for some $i$ than their contribution to \eqref{eq:lem_bound_intervals_proof} is zero and thus this case reduces to the case $n= N-2$. A similar reduction holds if $x_N, x_{N-1} \to -\infty$, $x_1, x_2 \to \infty$, or  $x_i, x_{i+1}$ for some $i$. It is left to consider the cases:

@@

\item[(1)]  $x_N \to -\infty$.
\item[(2)] $x_1 \to \infty$.

@@

Under case (1) we have
Assume first $x_N \rightarrow -\infty$. Then 

@@

\frac{ \left( \delta_N \right)^{2+\delta}} 
{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  }
 = \frac{ \left(  \sum_{k=1}^{N-1} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
{\left( \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- \sum_{k=1}^{N-1} (-1)^{k+1} F(x_k)  \right)^{1+\delta} } ,

@@

which is smaller than $\eta_\delta(0)$ by the induction hypothesis. Assume now that $x_1 \rightarrow \infty$. Then 

@@

& \frac{ \left( \delta_N \right)^{2+\delta}} 
{\left(\Delta_N \right)^{1+\delta}\left(1- \Delta_N \right)^{1+\delta}  } \\
=
& \frac{ \left(  \sum_{k=2}^{N} (-1)^{k+1}f(x_k) \right)^{2+\delta}} 
{\left( 1 + \sum_{k=2}^{N} (-1)^{k+1} F(x_k) \right)^{1+\delta}\left(1- 1 - \sum_{k=2}^{N} (-1)^{k+1} F(x_k)  \right)^{1+\delta} }  \\
& = \frac{ \left(  -\sum_{m=1}^{N} (-1)^{m+1}f(x'_m) \right)^{2+\delta}} 
{\left( 1 - \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m}) \right)^{1+\delta}\left( \sum_{m=1}^{N-1} (-1)^{m+1} F(x'_{m})  \right)^{1+\delta} },

@@

where $x'_{m} = x_{m+1}$ for $m=1,\ldots, N-1$. The last expression is also smaller than $\max_i \eta_\delta (x_i)$ by the induction hypothesis.  \par
It is left to consider the case where $c'(x)$ is not necessarily strictly decreasing. We approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin. For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function. Then $c_\alpha(x)$ is concave, symmetric, and differentiable with

>>>>

Consider the minimal MSE $D^\star$ in the Gaussian CEO setting with $L$ observers and under a total sum-rate $R_\Sigma = R_1 + \ldots +R_L$
from \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
R_{\Sigma} = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case of $R_\Sigma = n$ and $L=n$, we get
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
$D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describing the MSE under an optimal allocation of the sum-rate $R_\Sigma = n$ among the $n$ encoders. Therefore, this $D^\star$ provides a lower bound to the CEO MSE with $R_1=\ldots,R_n = 1$ and hence a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting. By considering $D^\star$ in \eqref{eq:ceo_optimal_sumrate2} as $n\rightarrow \infty$, we see that 
\[
D^\star = \frac{ 4\sigma^2 }{3n + 4 \sigma^2 / \sigma_\theta^2 } + o(n^{-1}) =  \frac{4\sigma^2}{3n} + o(n^{-1}). 
\]
We note that although the lower bound \eqref{eq:ceo_bound} was derived assuming the optimal allocation of $n$ bits per observation among the encoders, this bound cannot be tightened by considering the CEO MSE while enforcing the condition $R_1=\ldots = R_n = 1$. Indeed, an upper bound for the CEO MSE under the condition $R_1=\ldots = R_n = 1$ follows from \cite{KipnisRini2019}, and leads to
\[
D^\star \leq  \left( \frac{1}{\sigma_\theta^2} +  \frac{3n}{4\sigma^2 + \sigma_\theta^2} \right)^{-1}   =
\frac{4 \sigma^2}{3n} +  \frac{\sigma_\theta^2}{3n} + O(n^{-2}),
\]
which is equivalent to \eqref{eq:ceo_bound} when $\sigma_\theta$ is small.

\subsection{Proof of Theorem~\ref{thm:adpative_lower_bound}
\label{proof:thm:adpative_lower_bound}
}
Consider the following two Lemmas:
\begin{lem} \label{lem:bound_intervals}
Let $f(x)$ be log-concave, symmetric, and differentiable density function such that Assumption~1 holds. For any $x_1 \geq \ldots \geq x_n \in \R$ and $\delta>0$,
\begin{equation}
\frac{ \left| \sum_{k=1}^n (-1)^{k+1} f(x_k) \right|^2 }
{\left( \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) \left(1- \sum_{k=1}^n (-1)^{k+1} F(x_k) \right) } 
\leq  4f^2(0). 
\label{eq:lem_bound_intervals}
\end{equation}
\end{lem}
\begin{lem} \label{lem:fisher_bound}
Let $X$ be a random variable with a symmetric, log-concave, and continuously differentiable density function $f(x)$ such that Assumption~1 holds. For a Borel measurable $A$ set, 
\[
B(X) = \begin{cases} 1,& X \in A, \\
-1, & X \notin A.
\end{cases}
\]
Then the Fisher information of $B$ with respect to $\theta$ is bounded from above by $\eta(0)$.
\end{lem}

@@

We now finish the proof of Theorem~\ref{thm:adpative_lower_bound}. In order to bound from above the Fisher information of any set of $n$ one-bit messages with respect to $\theta$, we first note that without loss of generality, each message $B_i$ can is of the form
\begin{equation}
\label{eq:general_messages}
B_i = \begin{cases}
X_i \in A_i & 1, \\
X_i \notin A_i & -1,
\end{cases} 
\end{equation}
where $A_i \subset \R$ is a Borel measurable set. 
%Indeed, any measurable function $(X_i) \in \{-1,1\}$ can be written in the form \eqref{eq:general_messages} with $A_i = B^{-1}(1)$.
Consider the conditional distribution $P({B^n|\theta})$ of $B^n$ given $\theta$. We have 
\begin{align}
P\left( B^n | \theta \right) & =  \prod_{i=1}^n P\left(B_i | \theta, B^{i-1} \right), \label{eq:adpt_lower_bound_proof:1}
\end{align}
where $P\left(B_i =1 | \theta, B^{i-1}  \right) = \mathbb P\left( X_i \in A_i\right)$, so that the Fisher information of $B^n$ with respect to $\theta$ is given by 
\begin{align}
I_\theta(B^n) = \sum_{i=1}^n I_\theta (B_i|B^{i-1}),
\label{eq:fisher_information}
\end{align}
where $I_\theta (B_i|B^{i-1})$ is the Fisher information of the distribution of $B_i$ given $B^{i-1}$. From Lemma~\ref{lem:fisher_bound} it follows that $I_\theta (B_i|B^{i-1}) \leq 4f^2(0)$. The Van Trees inequality \cite{van2004detection, gill1995applications} now implies 
\begin{align*}
\ex{ \left( \theta_n - \theta \right)^2} &  \geq \frac{1}{ \ex{ I_\theta(B^n)} + I_0} \\
& = \frac{1}{ \sum_{i=1}^n I_\theta (B_i | B^{i-1} ) + I_0} \\
& \geq \frac{1}{ 4f^2(0) n + I_0}.
\end{align*}
\QEDA

@@

\begin{lem} \label{lem:bound_intervals_delta}
Let $f(x)$ be log-concave, symmetric, and differentiable density function. Let $\delta\geq 0$. Assume that the origin $x=0$ uniquely maximizes the function
\[
\eta_\delta(x) \triangleq  \eta^{1+\delta}(x)/f^\delta(x) = \frac{  \left( f(x) \right)^{2+\delta}}{\left(F(x)(1-F(x))\right)^{1+\delta}}
\]
and that $\eta_\delta(x)$ is non-increasing in $|x|$. For any $x_1 \ge \ldots \ge x_n \in \R^n$,
\begin{equation}
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{k=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq  \max_{i} \eta_\delta(x_i).
\label{eq:lem_bound_intervals_delta}
\end{equation}
\end{lem}
In particular, 
\[
\frac{ \left| \sum_{i=1}^n (-1)^{i+1} f(x_i) \right|^{2+\delta} }
{\left| \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} \left|1- \sum_{i=1}^n (-1)^{i+1} F(x_i) \right|^{1+\delta} } 
\leq \eta_\delta(0)
\]
since $\eta_\delta(x)$ attains its maximum at the origin.

@@

\delta_n(x_1,\ldots,x_n) \triangleq \sum_{i=1}^{n} s_i f(x_i),

@@

 \Delta_n(x_1,\ldots,x_n) \triangleq  \sum_{i=1}^n s_i F(x_i), 

@@

where $s_i \triangleq (-1)^{i+1}$. Set

@@

\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
{\left|\Delta_n(x_1,\ldots,x_n)  \left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} }.

@@

We use induction on $n \in \N$ to show that 
\label{eq:lemm:interval_bounds:to_show}
\frac{ \left| \delta_n(x_1,\ldots,x_n) \right|^{2+\delta}} 
{\left|\Delta_n(x_1,\ldots,x_n)\left(1- \Delta_n(x_1,\ldots,x_n) \right) \right|^{1+\delta} } \leq \max_{i}\eta_{\delta}(x_i).
 Since 

@@

\eta_\delta(x) =  \frac{  \left|\delta_1(x) \right|^{2+\delta}}{\left|\Delta_1(x)
(1-\Delta_1(x)) \right|^{1+\delta}}, 

@@

The case $n=1$ is trivial.  
%follows from the assumption that $\eta_\delta(x)$ is non-increasing in $|x|$. 
Assume that \eqref{eq:lemm:interval_bounds:to_show} holds for all integers up to $n = N$ and for any $x_1 \ge \ldots \ge x_n$. Consider the case $n = N+1$. Let $i^*$ be the index such that $x_{i^*}$ has minimal absolute value among $x_1,\ldots,x_N$. The assumption on $\eta_\delta(x)$ implies that
\eta_\delta(x_{i^*}) = \max_i \eta_\delta(x_i).
Since the LHS of \eqref{eq:lem_bound_intervals_delta} is invariant to a sign flip of all $x_1,\ldots,x_{N+1}$, we may assume that $x_{i^*}$ is positive without loss of generality. 
%For simplicity, we also assume that $s_{i^*} = 1$ and note that the case $s_{i^*} = -1$ is obtained using identical arguments. 
Set $x^* = x_{i^*}$ and let $k=i^*-1$. In what follows, variables with subscript of non-positive index are ignored in summations and in lists of arguments to functions. Consider the function
& g(y_1,\ldots,y_N) \triangleq  \frac{\left| \delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N) )\right|^{2+\delta}}{
\left|\Delta_N(y_1,\ldots,y_k,x_{i^*},y_{k+1}\ldots,y_N)  \right) \left(1 -\Delta_N(y_1,\ldots,y_k,x^*,y_{k+1}\ldots,y_N))  \right|^{1+\delta}
} .
The claim in the lemma is obtained by taking $y_i=x_{i'}$ where $i'$ is the $i$th element in $\{1,\ldots,N+1\}\setminus \{i^*\}$. It is therefore enough to prove that 
\max_{(y_1,\ldots,y_N) \in A_N} g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*),
A_N(x^*,k) \triangleq \left\{ (y_1,\ldots,y_N) \in \R^N\, : \, y_1 \ge y_k \ge x^* \ge -x^* \ge y_{k+1} \ldots \ge y_N
\right\}.

@@

Since $f(x)$ is log-concave, symmetric, and differentiable, we may write $f(x) = e^{c(x)}$ where $c(x)$ is concave, symmetric, and differentiable with derivative 
c'(x) \triangleq \frac{f'(x)}{f(x)} 
that is non-increasing. We first prove the lemma under the assumption that $c'(x)$ is an injection, or, equivalently, that $c(x)$ is strictly decreasing for all $x\in \R$. \par
The maximal value of $g(y_1,\ldots,y_N)$ is attained for the same $(y_1,\ldots,y_N) \in A_{N+1}(x^*,k)$ that maximizes

@@

 \log(g)(y_1,\ldots, y_N) =  (2+\delta) \log \left( \delta_N  \right)  - (1+\delta) \log \left( \Delta_N  \right) - (1+\delta) \log \left(1 - \Delta_N \right),

@@

where in the last display and henceforth we suppress the arguments $y_1,\ldots,y_k,x^*,y_{k+1},\ldots, y_N$ of the functions $\delta_N$ and $\Delta_N$.
The partial derivative of $\log(g)(y_1,\ldots,y_N)$ with respect to $y_i$ within the interior of $A_N(x^*,k)$ is given by

@@

\frac{\partial \log(g)}{\partial y_i} = \frac{(2+\delta) s_i f'(x_i)}{\delta_N } -\frac{(1+\delta) s_i f(x_i)}{\Delta_N  } + \frac{(1+\delta)s_i f(y_i)}{1-\Delta_N }.

@@

We conclude that the gradient of $\log(g)$ vanishes if and only if

@@

c'(y_i) = \frac{f'(y_i)}{f(y_i)} = \frac{1+\delta}{2+\delta} \frac{\delta_N}{2} \left( \frac{1}{\Delta_N} - \frac{1}{1-\Delta_N } \right),\quad i=1,\ldots,N.

@@

Since we assumed that $c'(x)$ is an injection, \eqref{eq:gradient_zero} is satisfied if and only if $y_1 = \ldots = y_N$. In this case, 
$g(y_1,\ldots,y_N) = \eta_\delta(x_{i^*})$  
if $N$ is even, or
& g(y_1,\ldots,y_N) = \frac{\left| s_1f(y_1)+s_{N+1}f(x_{i^*})  \right|^{2+\delta}} { 
\left|  s_1F(y_N) + s_{N+1}F(x_{i^*}) \right|^{1+ \delta} 
\left| 1 - (s_1F(y_1) + s_{N+1}F(x_{i^*})) \right|^{1+ \delta} } 
if $N$ is odd and $y_1 < x^*$. Form the induction assumption, the last display is bounded from above by $\eta_\delta(x_{i^*})$. The case where $N$ is odd and $y_1 > x^*$ is similar. 
We now consider the possibility that the maximum of $g(y_1,\ldots,y_N)$ is attained at the boundaries of $A_N(x^*,k)$. For boundary points for which $y_i = y_{i+1}$ for some $i$, the contribution of $y_i$ and $y_{i+1}$ to $g(y_1,\ldots,y_N)$ is zero and the induction assumption for $n=N-1$ implies that 
g(y_1,\ldots,y_N) \leq \eta_{\delta}(x^*)
at these points. The remaining boundary points of $A_N(x^*,k)$ are covered by the following cases:

@@

\item[(1)]  $y_N \to -\infty$. 
\item[(2)] $y_1 \to \infty$.
\item[(3)] $y_k = x_{i^*}$.
\item[(4)] $y_{k+1} = -x_{i^*}$. 

@@

For case (1), 

@@

g(y_1,\ldots,y_N) \to \frac{ \left| \sum_{i=1}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i f(y_i) \right|^{2+\delta}} 
{\left| \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right|^{1+\delta}\left|1- \left( \sum_{i=1}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N-1} s_i F(y_i) \right)  \right|^{1+\delta} },

@@

which is smaller than $\eta_\delta(x_{i^*})$ by the induction hypothesis. Similarly, under case (2),

@@

& g(y_1,\ldots,y_N) \to 
\frac{ \left| \sum_{i=2}^{k} s_i f(y_i) + s_{i^*} f(x_{i^*}) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
{\left| 1+ \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta}\left|-\left( \sum_{i=2}^{k} s_i F(y_i) + s_{i^*} F(x_{i^*}) - \sum_{i=k+1}^{N} s_i F(y_i) \right)  \right|^{1+\delta} },
 \\
& = \frac{ \left| -\sum_{i=2}^{k} s_i f(y_i) - s_{i^*} f(x_{i^*}) + \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
{ \left|1 - \left(-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right) \right|^{1+\delta} 
\left|-\sum_{i=2}^{k} s_i F(y_i) - s_{i^*} F(x_{i^*}) + \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} }

@@

which is smaller than $\eta_{\delta}(x_{i^*})$ by the induction hypothesis. Under case (3), the terms in $\delta_N$ and $\Delta_N$ corresponding to $y_k$ and $x_{i^*}$ cancel each other. As a result,  $g(y_1,\ldots,y_N)$ reduces to an expression with $n=N-1$ variables hence this case is handled by the induction hypothesis. 
Under case (4), set 
d \triangleq s_k F(-x^*) + s_{i^*} F(x^*) = s_{i^*}\left(1-2F(-x^*) \right), 
\sigma \triangleq \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i). 
\Sigma \triangleq \sum_{i=1}^{k-1} s_i F(y_i) - \sum_{i=k+1}^{N} s_i F(y_i). 
We have
& g(y_1,\ldots,y_N) =\nonumber  \\ 
\frac{ \left| \sum_{i=1}^{k-1} s_i f(y_i) - \sum_{i=k+1}^{N} s_i f(y_i) \right|^{2+\delta}} 
{\left| \sum_{i=1}^{k-1} s_i F(y_i) + d(x^*) - \sum_{i=k+1}^{N} s_i F(y_i) \right|^{1+\delta} \left|1- \sum_{i=1}^{k-1} s_i F(y_i) - d(x^*) + \sum_{i=k+1}^{N} s_i F(y_i)   \right|^{1+\delta} }, \\
& = \frac{ \left| \sigma \right|^{2+\delta}} 
{\left| \Sigma+d \right|^{1+\delta} \left|1- \Sigma - d \right|^{1+\delta} }  =  
\frac{ \left| \sigma \right|^{2+\delta}} 
{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} }  \left| \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \right|^{1+\delta}. 
By the induction hypothesis,
\frac{ \left| \sigma \right|^{2+\delta}} 
{\left| \Sigma \right|^{1+\delta} \left|1- \Sigma \right|^{1+\delta} } \leq \eta_\delta(x^*), 
hence it is left to show that 
 \frac{\Sigma(1-\Sigma) } { \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} \leq 1.
Note that whenever $d>0$, 
& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \geq d, 
while for $d<0$,
& \frac{ \Sigma(1-\Sigma) + d(1-2\Sigma)-d^2} {\Sigma(1-\Sigma)} \geq 1 \Leftrightarrow  1-2\Sigma \leq d. 
Therefore, it is enough to show that $\Sigma \leq F(-x^*)$ if $s_{i^*}=1$ and 
$\Sigma \geq F(-x^*)$ if $s_{i^*}=-1$. 
Indeed, if $s_{i^*}=1$, then $s_{k+1}=-1$ and monotonicity of $F(x)$ implies that 
\Sigma + d \leq F(y_1) - F(y_k) + F(x^*) - F(-x^*) + F(y_{k+2}) - F(y_N), 
and hence
\Sigma \leq 1-F(x^*) = F(-x^*). 
Similarly, if $s_{i^*}=-1$ then 
1 - \Sigma \leq 1 -  F(-x^*).
This conclude the proof in the case where $c'(x)$ is an injection. 
\par  
In the case where $c'(x)$ is not necessarily strictly decreasing, we approximate $c(x)$ using another concave symmetric function whose derivative is always negative except at the origin. For $\alpha>0$ consider the function  $f_\alpha(x) = \kappa(\alpha) e^{\sgn(c(x))|c(x)|^{1+\alpha}}$, where $\kappa(\alpha)$ is chosen such that $f_\alpha(x)$ is a probability density function. Then $c_\alpha(x)$ is concave, symmetric, and differentiable with
